Fractional Types

### 2016-12-19 typespp.tex

Given a \textrm{/-combinator} $p : \#c \leftrightblackspoon \#d$ which is a
morphism in the compact closed category, we have a dual morphism
$p^{\ast} : 1/\#d \leftrightblackspoon 1/\#c$. This is shown by building a
reversible circuit in Fig.~\ref{fig:dual}.

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
    \path (-1,1) edge node[above] {\footnotesize{$1/{\textsf{\#d}}$}} (0,1);

@@

We also show circuits that construct the \texttt{name} $\ulcorner{p}\urcorner$
and \texttt{coname} $\llcorner{p}\lrcorner$ of $p$, in
Fig.~\ref{fig:name-coname}.

>>>>

Given a \textrm{/-combinator} $p : \#c \leftrightblackspoon \#d$,
we can define a \emph{dual morphism}
$p^{\ast} : 1/\#d \leftrightblackspoon 1/\#c$. This is shown by building a
reversible circuit in Fig.~\ref{fig:dual}.  The highlights that seem to
``escape'' the circuit indicate that \emph{dual} can only be used in a
context with at least one quantifier being present.

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
    \path [highlight] (-1,1) edge node[above] {} (0,1);
    \path (-1,1) edge node[above] {\footnotesize{$1/{\textsf{\#d}}$}} (0,1);

@@

We also show circuits that construct the \texttt{name} $\ulcorner{p}\urcorner$
and \texttt{coname} $\llcorner{p}\lrcorner$ of $p$, in
Fig.~\ref{fig:name-coname}.  Like with dual, we need to insert a combinator $p$
\emph{under} a quantifier.
